Normalized expressions

### 2021-03-22 analysis/normalized.Rmd
Add results of manual inspection of 20 sites with only values

```{r setup, include=FALSE}
library(tidyverse)
library(fst)
library(fs)
library(DT)
library(scales)
library(corrr)

@@

@@

@@

We compute the sites which are at least one given a `V` minimized expression. Then we look at whether they are passed the default envir or not, and if there are variables in

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(fst)
library(fs)
library(DT)
library(scales)
library(corrr)
library(boot)

@@

# Variables

The percentage of non-default envir for variables seem to be quite low for the use-case. What if we remove more complex expressions and just keep the symbols?

```{r}
var_minimized <- E_cano %>% filter(minimized == "X")
nb_var_min_sites <- var_minimized %>% pull(src_ref) %>% n_distinct()

var_symb <-  E_cano %>% filter(minimized == "X", type == "symbol")
nb_var_symb_sites <- var_symb %>% pull(src_ref) %>% n_distinct()

var_symb_non_default_envir <- var_symb %>% filter(!is.na(envir))
nb_var_symb_ndefault_sites <- var_symb_non_default_envir %>% pull(src_ref) %>% n_distinct()

r("nb non default envir variables percent", ratio(nb_var_symb_ndefault_sites, nb_var_symb_sites))
```

@@

And the results of the manual inspection:

```{r, include=FALSE}
useful_percent <- 0
```

```{r, eval=dataset_name == "package"}
manual_value_necessary <- read_csv(path(params$base_dir, "non-necessary-value-evals.csv"), col_types = cols(src_ref = col_character(), necessary = col_logical()))

statistic <- function(data, i) {
  df <- data[i,] %>% select(necessary) %>% filter(necessary)
  nrow(df) / nrow(data[i,])
}

bootstrap <- boot(manual_value_necessary, statistic, R = 1000)

useful_percent <- mean(bootstrap$t, na.rm = TRUE)

r("useful value eval percent", percent(useful_percent))
```

`r percent(useful_percent)`% of those `eval` are useful.

@@

We compute the sites which are at least one given a `V` minimized expression. Then we look at whether they are passed the default envir or not, and if there are variables in:
